\cvsection{Academic Project}
\begin{cventries}

 %%%Twitter QA%%%
      \cventry
    {Keywords: Information Retrieval, Social Network, Neo4j, Twitter, Java} % keywords
    {Find the Right Answerers for Twitter Questions} % subject
    {} % date
%     {Feb. 2015 - Apr. 2015} % date 
    {} 
    {
      \begin{cvitems}
      % \item {Designed and implemented an interactive system for recommending the answers for Twitter questions.}
      	\item {Designed and implemented an interactive system to get the question and pass it to backend, and finally display the results.}
		\item {Planed and built a backend system to crawled and parse the questioner's information and its follower's timeline using Java.}
        \item {Developed a storage system to store crawled tweets data and social relations of twitter users through Neo4j.}
%         \item{Crawled tweets data and stored them and build social relations of twitter users through Neo4j.}
%         \item {Used Twitter API to crawl tweets data and built social relations of twitter users by Neo4j. }
%         \item {Represented text as graph using unigram language model and built relations between text and user.}
%         \item {Implemented probability language model and tried various smoothing methods.}
      \end{cvitems}
    }



%%%Springleaf Data mining%%%
  \cventry
    {Keywords: Data Mining, Classification, XGBoost, R, Python} % keywords
    {Springleaf Marketing Response } % subject
    {} % date
%     {Oct. 2015 - Dec. 2015}  % date 
    {} 
    {
      \begin{cvitems}
      	\item {Designed and built a data mining model to determine whether to send a direct mail piece to targeted customers.}
        \item {Preprocessed high-dimensional data and applied feature selection methods to reduce dimensions by more than 50\%. }
%         \item { Preprocessed high-dimensional data, including missing values, time series and other messy features.}
%         \item { Tried feature selection methods, such as feature ranking and subset selection.}
        \item {Applied gradient boost trees using XGBoost package, to improve the area under the ROC curve by 0.75.}
      \end{cvitems}
    }

 
 
%%% Graph Search %%%
    \cventry
    {Keywords: Graph Search, AWS, REST API, Neo4j, Maven, open-source, Java} % keywords
    {MultiDBs: Keyword Search Graph} % subject
    {} % date
%     {Feb. 2015 - Apr. 2015} % date 
    {} 
    {
      \begin{cvitems}
      	\item {Designed and deployed a keyword search system to search all related results based on graph database.}
        \item {Reduced time-cost by 20\%, compared with relational database search engine.}
        \item {Implemented a storage system using Neo4j to store a bunch of distributed heterogeneous data sources, such as RDBMS and data files, through Spring framework; developed REST API to deal with REST requests from other projects of MultiDBs.}
%         \item {	Received data from RDBMS via REST API, transformed and stored the data into Neo4j automatically. }
%         \item {	Designed webpage on Spring framework to connect Neo4j, did keyword search and returned all related results.}
%         \item {	Deployed the system on AWS}
      \end{cvitems}
    }
    
%%% Yelp Data Challenge %%%
  \cventry
    {Keywords: NLP, Text Summarization, Yelp Dataset Challenge, Python}  % keywords
    {Tips Generation for Yelp Reviews} % subject
    {} % date
%     {Feb. 2016 - Apr. 2016}  % date
    {}
    {
      \begin{cvitems}
        \item {Built representations of the review sentences, such as Word2vec, LDA and TF-IDF, through NLTK and other python packages.}
        \item {Implemented density based method ,Sentence Clustering, and graph-based ranking model, TextRank, to extract tips, Evaluated the performance of system extracted tips by ROUGE and BLUE.}
%         \item {Evaluated the performance of system extracted tips by ROUGE and BLUE.}
      \end{cvitems}
    }

% %%% Visualization %%%
%   \cventry
%     {Keywords: Visualization, d3.js, Javascript, HTML, CSS} % keywords
%     {Data Visualization on Contagious Diseases} % subject
%     {} % date
% %     {Oct. 2014 - Dec. 2014}  % date 
%     {} 
%     {
%       \begin{cvitems}
% 		\item {Devised and assembled an interactive visualization system to explore the data of three major contagious diseases.}
%         \item {Implemented interactive front end using Javascript; developed three major methods using d3.js, choropleth, bar chart and line chart, to visualize the change of vaccine data over years and distribution among states.}
%       \end{cvitems}
%     }


% %%% Database project %%%
%     \cventry
%     {Keywords: Java, MySQL, MVC, JSP} % keywords
%     {Online Digital Store} % subject
%     {} % date
% %     {Oct. 2014 - Dec. 2014} % date 
%     {} 
%     {
%       \begin{cvitems}
%         \item {Designed and built an online E-business system to sell digital products by using JSP and Servlet in MVC framework.}
%         \item {Designed E-R diagram, designed and implemented backend database using MySQL according to business needs.}
%         \item {Implemented interactions between front end and back end.}
%       \end{cvitems}
%     }
    
\end{cventries}